Catchy Title Goes Here

### 2018-06-06 Paper/paper.tex
Figures code and paper updated

@@

@@

This Figure shows the posterior distributions and assumed values for $\gamma$ from simulated datasets with four different values of $\gamma$. The top panel is generated by analyzing all three datasets, and the bottom panel using only case and vaccination data. In addition to the assumed values and the posteriors, we also show the prior on $\gamma$ as a yellow line. In the top panel we see, as expected, that the inferred values for $\gamma$ are systematically biased away from the injected values - they turn out to be consistently biased low in this case. Although this means that we do not necessarily infer an accurate value for vaccine efficacy with this data using this model, it is worth nothing that we do infer the correct \emph{ordering} for $\gamma$. That is, if these were four different locations, we would correctly identify the location with the lowest vaccine efficacy.

>>>>

FIX Need to add a description of the model including a constant, and a discussion of the fact that we end up using this for the real datasets in many cases.

@@

\subsection{Model Comparison}
For the real data from the DRC, we wish to determine which provinces warrant the more complicated seroprevalence model from Sec.~\ref{subsec:CompetingRates} that includes a constant in addition to the Weibull function, and which are described sufficiently by a constant force of infection alone. To do this, we calculate the Bayes factor between the two models, which, given that our prior belief in the two models is equal, is simply the ratio of the evidence for each of the models. The evidence is the fully marginalized likelihood (FML), and can often be quite difficult to calculate accurately. Luckily for us, the two models in question are nested - we recover the constant-only model when $\alpha = 1.0$ -  and so we can use a technique called the Savage-Dickey density ratio.

Two models, $\mathcal{M}_0$ and $\mathcal{M}_1$, where $\mathcal{M}_0$ is the simpler model, are nested when there exists a parameter $\omega$ for which $\mathcal{M}_0 = \mathcal{M}_1$ when $\omega = \omega_0$. (For us, constant is the same as Weibull plus constant when the parameter $\alpha$ is equal to 1.0). In this case, the Bayes factor between $\mathcal{M}_0$ and $\mathcal{M}_1$ is simply
\begin{equation}
BF_{01} = \frac{\rm{posterior}(\omega =\omega_0)}{\rm{prior}(\omega=\omega_0},
\end{equation}
where posterior() and prior() refer to the posterior and prior densities at $\omega = \omega_0$. To evaluate this quantity, it is only necessary to generate the posterior distribution of $\omega$, and then compare the posterior and prior densities.

We generate these distributions for each province independently using Markov chain Monte Carlo techniques, described in the next section, and find that only three provinces are adequately described by the constant force of infection model: Bandundu, Kasai Occidental, and Maniema. The rest of the provinces require the more complicated Weibull plus constant model. For all of the results presented in Sec.~\ref{sec:Results}, we use these models as noted here for each of the provinces.

@@

This Figure shows the posterior distributions and assumed values for $\gamma$ from simulated datasets with four different values of $\gamma$. The top panel is generated by analyzing all three datasets, and the bottom panel using only case and vaccination data. In addition to the assumed values and the posteriors, we also show the prior on $\gamma$ as a yellow line. In the top panel we see, as expected, that the inferred values for $\gamma$ are systematically biased away from the injected values - they turn out to be consistently biased low in this case. Although this means that we do not necessarily infer an accurate value for vaccine efficacy with this data using this model, it is worth noting that we do infer the correct \emph{ordering} for $\gamma$. That is, if these were four different locations, we would correctly identify the location with the lowest vaccine efficacy.
